### 2024-09-29 cognitive-bias.qmd
20240929 - addressing cognitive biases

>>>>

In general, when faced with a situation in which bias is likely, @Kahneman2011 advises slowing down, being thoughtful and deliberate, questioning your intuitions, and imposing orderly procedures, such as checklists, reference-class forecasting, and a "premortem".
A premortem is when you consider, in advance of the decision, what likely went wrong if the decision were to work out terribly.
Reference-class forecasting involves examining a reference class of similar projects to identify the most likely range of outcomes for the project.
